---
title: "free reward response"
author: "Robert Hickman"
---
title: "fractal display response"
author: "Robert Hickman"
date: "2025-03-12"
output: html_document
---

```{r setup, warning=FALSE,message=FALSE}
rm(list = ls())
set.seed(3459)
setwd("~/projects/thesis_scripts/figure_scripts/fractal_display/")
library(tidyverse)
library(jsonlite)
library(patchwork)
library(svglite)
library(viridis)
source("../../src/neuron_smoothing.R")
source("../../src/figs.R")

monkey_fill_pal <- scale_fill_manual(values = c("royalblue", "darkorange"), labels = c("Monkey U", "Monkey V"), guide = FALSE)
monkey_col_pal <- scale_colour_manual(values = c("royalblue", "darkorange"), labels = c("Monkey U", "Monkey V"), guide = FALSE)

neuronal_data <- bind_rows(
  readRDS("../../data/neurons/onefrac_noerror_neuronal_data.rds"),
  readRDS("../../data/neurons/threefrac_noerror_neuronal_data.rds"),
)
task_data <- readRDS("../../data/neurons/task_data.rds")

cell_baselines_fractals <-
  readRDS("../../data/baseline/cell_prefc_baselines_fractals_smoothed.rds")
cell_baselines_fractal_counts <-
  readRDS("../../data/baseline/cell_prefc_baselines_fractals.rds")
cell_baselines_counts <-
  readRDS("../../data/baseline/cell_prefc_baselines.rds")

sigcells_uly <-
  read_csv("../../data/cells/uly_sig_cells.csv") %>%
  mutate(monkey = "Monkey U") %>%
  mutate(date = as.Date(date, "%d-%b-%y"))
sigcells_vice <-
  read_csv("../../data/cells/vice_sig_cells.csv") %>%
  mutate(monkey = "Monkey V") %>%
  mutate(date = as.Date(date, "%d-%b-%Y"))

sigcells <-
  bind_rows(sigcells_uly, sigcells_vice) %>%
  mutate(cell = paste0("cell", gsub("^(Clust)([0-9])(_.*)$", "\\2", cluster)))

monkey_windows <- read_csv("../../data/config/monkey_windows.csv")
configs <- read_csv("../../data/config/configs.csv")

group_cols <- c("date", "monkey", "cell")
group_cols_fractal <- c(group_cols, "fractal_value")

relevant_cells <- sigcells %>%
  select(date, monkey, cell, isDA, isResponsive, numTrGood, DAFracResponsive) %>%
  filter(isDA == 1 & isResponsive == 1 & numTrGood == 1) %>%
  distinct(date, monkey, cell, .keep_all = TRUE)

n_start <- filter(configs, var == "neurons_start") %>% pull(value)
n_end <- filter(configs, var == "neurons_end") %>% pull(value)
smooth_window <-
  filter(configs, var == "smooth_window") %>% pull(value)
```



```{r population_fig}
pre_start <- -500
pre_end <- -50

fractal_displayed_task_data <- task_data %>%
  filter(situation %in% c(1,2,3)) %>%
  select(date, monkey, trial, fractal_value)

fd_bits <- neuronal_data %>%
  filter(situation %in% c(1,2,3)) %>%
  filter(map_lgl(bits, function(x) {
    if (!is.null(x) && is.data.frame(x) && nrow(x) > 0) {
      matching_rows <- x$names == "fractal_display" & x$index == "upat"
      sum(matching_rows) == 1 && !is.na(x$vals[matching_rows])
    } else {
      FALSE
    }
  })) %>%
  unnest(bits) %>%
  filter(names == "fractal_display" & index == "upat")

fd_spikes <- fd_bits %>%
  left_join(fractal_displayed_task_data, by = c("date", "monkey", "trial")) %>%
  select(date, monkey, trial, fractal_value, fd_time = vals, sorted_spikes) %>%
  unnest(sorted_spikes) %>%
  mutate(spike_bit_time_ms = trial_spike_time_ms - fd_time)

fd_baselines <- fd_spikes %>%
  filter(spike_bit_time_ms >= pre_start & spike_bit_time_ms <= pre_end) %>%
  select(date, monkey, cell, fractal_value, spike_bit_time_ms) %>%
  group_by(date, monkey, cell, fractal_value) %>%
  group_split() %>%
  map_df(get_baseline_params, w = smooth_window, t = pre_start:pre_end)

fractal_display_smoothed <- fd_spikes %>%
  filter(spike_bit_time_ms >= n_start &
           spike_bit_time_ms <= n_end) %>%
  inner_join(relevant_cells, by = group_cols) %>%
  select(date, monkey, cell, fractal_value, spike_bit_time_ms) %>%
  nest(vector = spike_bit_time_ms) %>%
  left_join(fd_baselines, by = group_cols_fractal) %>%
  group_by(across(all_of(group_cols_fractal))) %>%
  group_split() %>%
  map_df(smooth_data, start = n_start, end = n_end, 100) %>%
  group_by(monkey, t, fractal_value) %>%
  summarise(
    av_zscore = mean(z_score, na.rm = TRUE),
    sd_zscore = sd(z_score, na.rm = TRUE),
    n = n(),
    .groups = "keep"
  ) %>%
  mutate(sem = sd_zscore / sqrt(n)) %>%
  mutate(
    fractal_reward_value = case_when(
      fractal_value == 1 ~ "low",
      fractal_value == 2 ~ "medium",
      fractal_value == 3 ~ "high"
    )
  ) %>%
  mutate(fractal_reward_value = factor(fractal_reward_value, levels = c("high", "medium", "low")))

p_population_response <-
  ggplot(
    fractal_display_smoothed %>% filter(
      t > filter(configs, var == "fig_start") %>% pull(value) &
        t < filter(configs, var == "fig_end") %>% pull(value)
    ),
    aes(x = t, y = av_zscore, colour = fractal_reward_value)
  ) +
  geom_rect(
    data = monkey_windows,
    aes(
      xmin = window_start,
      xmax = window_end,
      ymin = -Inf,
      ymax = Inf
    ),
    fill = "grey",
    alpha = 0.5,
    inherit.aes = FALSE
  ) +
  geom_line() +
  scale_colour_manual(values = c("darkred", "darkgreen", "darkblue"),
                      name = "fractal reward value") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  facet_wrap(~ monkey, scales = "free") +
  population_firing_fig_theme(
    filter(configs, var == "fig_start") %>% pull(value),
    filter(configs, var == "fig_end") %>% pull(value),
    "fractal display"
  )

```

```{r pop stats test}
spike_counts <- fd_spikes %>%
  select(date, monkey, cell, trial, fractal_value, spike_bit_time_ms) %>%
  left_join(monkey_windows, by = "monkey") %>%
  group_by(date, monkey, cell, trial, fractal_value, window_start, window_end) %>%
  summarise(n = sum(spike_bit_time_ms >= window_start & spike_bit_time_ms <= window_end), .groups = "drop") %>%
  mutate(adj_n = n * (1000 / (window_end - window_start))) %>%
  right_join(relevant_cells, by = group_cols) %>%
  drop_na() %>%
  mutate(adj_n = replace_na(adj_n ,0)) %>%
  select(date, monkey, cell, trial, fractal_value, spike_counts = adj_n)
  
agg_spike_counts <- spike_counts %>%
  group_by(date, monkey, cell, fractal_value) %>%
  summarise(mean_spike_counts = mean(spike_counts), sem_spike_counts = sd(spike_counts) / sqrt(n()), n_trials = n(), .groups = "drop")


monkey_u_data <- subset(agg_spike_counts, monkey == "Monkey U")
monkey_v_data <- subset(agg_spike_counts, monkey == "Monkey V")

kw_u <- kruskal.test(mean_spike_counts ~ factor(fractal_value), data = monkey_u_data)
print("Kruskal-Wallis Test Results for Monkey U:")
print(kw_u)

kw_v <- kruskal.test(mean_spike_counts ~ factor(fractal_value), data = monkey_v_data)
print("Kruskal-Wallis Test Results for Monkey V:")
print(kw_v)


```

```{r population_fig}
bid_quintile_task_data <- task_data %>%
  filter(situation %in% c(1, 2, 3)) %>%
  select(date, monkey, trial, monkey_bid) %>%
  mutate(
    monkey_bid_quintile = case_when(
      monkey_bid <= 20 ~ 1,
      monkey_bid <= 40 ~ 2,
      monkey_bid <= 60 ~ 3,
      monkey_bid <= 80 ~ 4,
      TRUE ~ 5
    )
  )

fd_spikes <- fd_bits %>%
  left_join(bid_quintile_task_data, by = c("date", "monkey", "trial")) %>%
  select(date,
         monkey,
         trial,
         monkey_bid_quintile,
         fd_time = vals,
         sorted_spikes) %>%
  unnest(sorted_spikes) %>%
  mutate(spike_bit_time_ms = trial_spike_time_ms - fd_time)

fd_baselines <- fd_spikes %>%
  filter(spike_bit_time_ms >= pre_start &
           spike_bit_time_ms <= pre_end) %>%
  select(date, monkey, cell, monkey_bid_quintile, spike_bit_time_ms) %>%
  group_by(date, monkey, cell, monkey_bid_quintile) %>%
  group_split() %>%
  map_df(get_baseline_params, w = smooth_window, t = pre_start:pre_end)

fractal_display_smoothed <- fd_spikes %>%
  filter(spike_bit_time_ms >= n_start &
           spike_bit_time_ms <= n_end) %>%
  inner_join(relevant_cells, by = group_cols) %>%
  select(date, monkey, cell, monkey_bid_quintile, spike_bit_time_ms) %>%
  nest(vector = spike_bit_time_ms) %>%
  left_join(fd_baselines, by = c(group_cols, "monkey_bid_quintile")) %>%
  group_by(across(all_of(c(
    group_cols, "monkey_bid_quintile"
  )))) %>%
  group_split() %>%
  map_df(smooth_data, start = n_start, end = n_end, 100) %>%
  group_by(monkey, t, monkey_bid_quintile) %>%
  summarise(
    av_zscore = mean(z_score, na.rm = TRUE),
    sd_zscore = sd(z_score, na.rm = TRUE),
    n = n(),
    .groups = "keep"
  ) %>%
  mutate(sem = sd_zscore / sqrt(n))

p_population_response_quintiles <-
  ggplot(
    fractal_display_smoothed %>% filter(
      t > filter(configs, var == "fig_start") %>% pull(value) &
        t < filter(configs, var == "fig_end") %>% pull(value)
    ),
    aes(
      x = t,
      y = av_zscore,
      colour = factor(monkey_bid_quintile)
    )
  ) +
  geom_rect(
    data = monkey_windows,
    aes(
      xmin = window_start,
      xmax = window_end,
      ymin = -Inf,
      ymax = Inf
    ),
    fill = "grey",
    alpha = 0.5,
    inherit.aes = FALSE
  ) +
  geom_line() +
  scale_colour_manual(values = viridis::inferno(5, begin = 0, end = 0.8),
                      name = "forthcoming bid quintile (5 highest)") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  facet_wrap(~ monkey, scales = "free") +
  population_firing_fig_theme(
    filter(configs, var == "fig_start") %>% pull(value),
    filter(configs, var == "fig_end") %>% pull(value),
    "fractal display"
  )

```

```{r}
spike_counts <- fd_spikes %>%
  select(date, monkey, cell, trial, monkey_bid_quintile, spike_bit_time_ms) %>%
  left_join(monkey_windows, by = "monkey") %>%
  group_by(date, monkey, cell, trial, monkey_bid_quintile, window_start, window_end) %>%
  summarise(n = sum(spike_bit_time_ms >= window_start & spike_bit_time_ms <= window_end), .groups = "drop") %>%
  mutate(adj_n = n * (1000 / (window_end - window_start))) %>%
  right_join(relevant_cells, by = group_cols) %>%
  drop_na() %>%
  mutate(adj_n = replace_na(adj_n ,0)) %>%
  select(date, monkey, cell, trial, monkey_bid_quintile, spike_counts = adj_n)
  
agg_spike_counts <- spike_counts %>%
  group_by(date, monkey, cell, monkey_bid_quintile) %>%
  summarise(mean_spike_counts = mean(spike_counts), sem_spike_counts = sd(spike_counts) / sqrt(n()), n_trials = n(), .groups = "drop")


monkey_u_data <- subset(agg_spike_counts, monkey == "Monkey U")
monkey_v_data <- subset(agg_spike_counts, monkey == "Monkey V")

kw_u <- kruskal.test(mean_spike_counts ~ factor(monkey_bid_quintile), data = monkey_u_data)
print("Kruskal-Wallis Test Results for Monkey U:")
print(kw_u)

kw_v <- kruskal.test(mean_spike_counts ~ factor(monkey_bid_quintile), data = monkey_v_data)
print("Kruskal-Wallis Test Results for Monkey V:")
print(kw_v)
```


```{r}
ntiles = 25

bid_ntile_data <- task_data %>%
  filter(situation %in% c(1, 2, 3)) %>%
  select(date, monkey, session, trial, monkey_bid) %>%
  mutate(
    bid_ntiles = cut(
      monkey_bid,
      breaks = seq(0, 100, by = 100/ntiles),
      labels = FALSE,
      include.lowest = TRUE
    )
  )

relevant_cells_ntiles <- relevant_cells %>%
  select(all_of(group_cols)) %>%
  crossing(bid_ntiles = 1:ntiles)

fd_spikes <- fd_bits %>%
  left_join(bid_ntile_data, by = c("date", "monkey", "session", "trial")) %>%
  select(date, monkey, session, trial, bid_ntiles, fd_time = vals, sorted_spikes) %>%
  unnest(sorted_spikes) %>%
  mutate(spike_bit_time_ms = trial_spike_time_ms - fd_time) %>%
  left_join(monkey_windows, by = "monkey") %>%
  group_by(date, monkey, cell, session, trial, window_start, window_end, bid_ntiles) %>%
  summarise(n = sum(spike_bit_time_ms >= window_start & spike_bit_time_ms <= window_end), .groups = "drop") %>%
  mutate(adj_n = n * (1000 / (window_end - window_start))) %>%
  right_join(relevant_cells_ntiles, by = c(group_cols, "bid_ntiles")) %>%
  mutate(adj_n = replace_na(adj_n ,0)) 

fd_av_spikes <- fd_spikes %>%
  group_by(monkey, bid_ntiles) %>%
  summarise(mean_n_s = mean(adj_n), sem = sd(adj_n) / sqrt(n()), .groups = "drop") %>%
  mutate(bid_perc = bid_ntiles / ntiles)

regression_stats <- fd_av_spikes %>%
  group_by(monkey) %>%
  do(model = lm(mean_n_s ~ bid_perc, data = .)) %>%
  mutate(
    glance = list(broom::glance(model))
  ) %>%
  unnest(glance) %>%
  select(monkey, p.value, r.squared, adj.r.squared)

print(regression_stats)

p_regression <- ggplot(fd_av_spikes, aes(x = bid_perc, y = mean_n_s, colour = monkey, group = monkey)) + 
  stat_smooth(method = "lm") +
  geom_point(size = 2) + 
  geom_errorbar(aes(ymin = mean_n_s - sem, ymax = mean_n_s + sem), width = 0) +
  monkey_col_pal +
  labs(
    x = "monkey bid percentage",
    y = "average firing rate (impulses/s)"
  ) +
  theme_minimal() +
  facet_wrap(~ monkey) +
  theme(
    strip.background = element_blank(),
    strip.text = element_blank(),
    legend.position = "bottom"
  )

baselines <- cell_baselines_counts %>%
  inner_join(relevant_cells, by = group_cols) %>%
  group_by(date, monkey, cell, trial) %>%
  summarise(n = sum(spike_bit_time_ms >= -500 & spike_bit_time_ms <= 0), .groups = "drop") %>%
  mutate(adj_n = n * 2) %>%
  group_by(date, monkey, cell) %>%
  summarise(mean_n = mean(adj_n), sd_n = sd(adj_n), .groups = "drop") %>%
  filter(sd_n != 0)

fd_normalised_spikes <- fd_spikes %>%
  left_join(baselines, by = group_cols) %>%
  drop_na() %>%
  mutate(norm_n = (adj_n - mean_n) / sd_n) %>%
  group_by(monkey, bid_ntiles) %>%
  summarise(mean_n_s = mean(norm_n), sem = sd(norm_n) / sqrt(n()), .groups = "drop") %>%
  mutate(bid_perc = bid_ntiles / ntiles)

regression_stats_norm <- fd_normalised_spikes %>%
  group_by(monkey) %>%
  do(model = lm(mean_n_s ~ bid_perc, data = .)) %>%
  mutate(
    glance = list(broom::glance(model))
  ) %>%
  unnest(glance) %>%
  select(monkey, p.value, r.squared, adj.r.squared)

print(regression_stats_norm)

p_norm_regression <- ggplot(fd_normalised_spikes, aes(x = bid_perc, y = mean_n_s, colour = monkey, group = monkey)) + 
  stat_smooth(method = "lm") +
  geom_point(size = 2) + 
  geom_errorbar(aes(ymin = mean_n_s - sem, ymax = mean_n_s + sem), width = 0) +
  monkey_col_pal +
  labs(
    x = "monkey bid percentage",
    y = "normalised firing rate (impulses/s)"
  ) +
  theme_minimal() +
  facet_wrap(~ monkey) +
  theme(
    strip.background = element_blank(),
    strip.text = element_blank(),
    legend.position = "bottom"
  )

```
```{r}
#not normalised
monkey_u_data <- fd_av_spikes %>% filter(monkey == "Monkey U")
monkey_v_data <- fd_av_spikes %>% filter(monkey == "Monkey V")

monkey_u_model <- lm(mean_n_s ~ bid_perc, data = monkey_u_data)
u_summary <- summary(monkey_u_model)
print("Monkey U Regression Results:")
print(u_summary)
monkey_v_model <- lm(mean_n_s ~ bid_perc, data = monkey_v_data)
v_summary <- summary(monkey_v_model)
print("Monkey V Regression Results:")
print(v_summary)

# normalised
monkey_u_norm_data <- fd_normalised_spikes %>% filter(monkey == "Monkey U")
monkey_v_norm_data <- fd_normalised_spikes %>% filter(monkey == "Monkey V")

monkey_u_norm_model <- lm(mean_n_s ~ bid_perc, data = monkey_u_norm_data)
u_norm_summary <- summary(monkey_u_norm_model)
print("Monkey U Normalised Regression Results:")
print(u_norm_summary)
monkey_v_norm_model <- lm(mean_n_s ~ bid_perc, data = monkey_v_norm_data)
v_norm_summary <- summary(monkey_v_norm_model)
print("Monkey V Normalised Regression Results:")
print(v_norm_summary)

```

```{r}
joy_task_data <- readRDS("~/projects/thesis_scripts/data/old_behaviour/joystick_behaviour_paired_data.rds") %>%
  select(date, monkey, trial_no, subtask, starting_bid, monkey_bid, reward_level, data) %>%
  filter(subtask == "BDM") %>%
  mutate(monkey = case_when(
    monkey %in% c("Ulysses", "Monkey U", "monkey U") ~ "Monkey U",
    monkey %in% c("Vicer", "Monkey V", "monkey V") ~ "Monkey V",
  ))

joy_task_data$total_movement <- map_dbl(joy_task_data$data, function(j) sum(j$stimuli_movement, na.rm = TRUE))
joy_task_data$abs_total_movement <- map_dbl(joy_task_data$data, function(j) sum(abs(j$stimuli_movement), na.rm = TRUE))
joy_task_data$rt_ms <- map_dbl(joy_task_data$data, function(j) (first(which(j$stimuli_movement != 0)) / 60) * 1000)
joy_task_data$bid_place_ms <- map_dbl(joy_task_data$data, function(j) (last(which(j$stimuli_movement != 0)) / 60) * 1000)
joy_task_data$bid_time_ms <- joy_task_data$bid_place_ms - joy_task_data$rt_ms

```

```{r}
joy_task_data2 <- joy_task_data %>%
  mutate(time_param = bid_time_ms) %>%
  group_by(monkey) %>%
  mutate(
    time_10th = quantile(time_param, 0.2, na.rm = TRUE),
    time_90th = quantile(time_param, 0.8, na.rm = TRUE),
    net_10th = quantile(total_movement, 0.1, na.rm = TRUE),
    net_90th = quantile(total_movement, 0.9, na.rm = TRUE),
    gross_10th = quantile(abs_total_movement, 0.1, na.rm = TRUE),
    gross_90th = quantile(abs_total_movement, 0.9, na.rm = TRUE)
  ) %>%
  filter(
    time_param >= time_10th & time_param <= time_90th,
    total_movement >= net_10th & total_movement <= net_90th,
    abs_total_movement >= gross_10th & abs_total_movement <= gross_90th
  ) %>%
  mutate(
    net_movement = cut(
      total_movement,
      breaks = seq(min(net_10th), max(net_90th), length.out = ntiles + 1),
      labels = FALSE,
      include.lowest = TRUE
    ),
    gross_movement = cut(
      abs_total_movement,
      breaks = seq(min(gross_10th), max(gross_90th), length.out = ntiles + 1),
      labels = FALSE,
      include.lowest = TRUE
    ),
    movement_time = cut(
      time_param,
      breaks = seq(min(time_10th), max(time_90th), length.out = ntiles + 1),
      labels = FALSE,
      include.lowest = TRUE
    )
  ) %>%
  select(-ends_with("_10th"), -ends_with("_90th")) %>%
  ungroup() %>%
  select(date, monkey, trial = trial_no, net_movement, gross_movement, movement_time)

movement_residuals_data <- fd_spikes %>%
  left_join(baselines, by = group_cols) %>%
  drop_na() %>%
  mutate(norm_n = (adj_n - mean_n) / sd_n) %>%
  mutate(bid_perc = bid_ntiles / ntiles) %>%
  left_join(joy_task_data2, by = c("date", "monkey", "trial")) %>%
  dplyr::select(date, monkey, cell, trial, bid_perc, norm_n, net_movement, gross_movement, movement_time) %>%
  pivot_longer(cols = c(net_movement, gross_movement, movement_time), names_to = "movement_parameter", values_to = "movement_parameter_ntile")

movement_summary <- movement_residuals_data %>%
  group_by(monkey, movement_parameter, movement_parameter_ntile) %>%
  summarise(mean_n_s = mean(norm_n), 
            sem = sd(norm_n) / sqrt(n()), 
            .groups = "drop") %>%
  mutate(movement_perc = movement_parameter_ntile / ntiles)

bid_models <- movement_residuals_data %>%
  group_by(monkey) %>%
  do(model = lm(norm_n ~ bid_perc, data = .))

movement_residuals <- movement_residuals_data %>%
  group_by(monkey) %>%
  nest() %>%
  left_join(bid_models, by = "monkey") %>%
  mutate(
    residuals = map2(data, model, ~mutate(.x, residual = residuals(.y)))
  ) %>%
  select(monkey, residuals) %>%
  unnest(residuals)

residual_summary <- movement_residuals %>%
  group_by(monkey, movement_parameter, movement_parameter_ntile) %>%
  summarise(mean_residual = mean(residual),
            sem_residual = sd(residual) / sqrt(n()),
            .groups = "drop") %>%
  mutate(movement_perc = movement_parameter_ntile / ntiles) %>%
  mutate(movement_parameter_name = case_when(
    movement_parameter == "gross_movement" ~ "gross movement",
    movement_parameter == "net_movement" ~ "net movement",
    movement_parameter == "movement_time" ~ "bidding time",
  )) %>%
  mutate(movement_parameter_name = factor(movement_parameter_name, levels = c("gross movement", "net movement", "bidding time")))

p <- ggplot(residual_summary, aes(x = movement_perc, y = mean_residual, colour = monkey, group = monkey)) + 
  stat_smooth(method = "lm") +
  geom_point(size = 2) + 
  geom_errorbar(aes(ymin = mean_residual - sem_residual, ymax = mean_residual + sem_residual), width = 0) +
  monkey_col_pal +
  labs(
    x = "movement parameter percentile",
    y = "firing rate residual"
  ) +
  theme_minimal() +
  facet_grid(movement_parameter_name~ monkey, scales = "free_y") +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    legend.position = "bottom",
    strip.text.y = element_text(size = 12)
  )

residual_movement_stats <- residual_summary %>%
  group_by(monkey, movement_parameter) %>%
  do(model = lm(mean_residual ~ movement_perc, data = .)) %>%
  mutate(
    tidy = list(broom::tidy(model)),
    glance = list(broom::glance(model))
  )

residual_movement_coefs <- residual_movement_stats %>%
  unnest(tidy) %>%
  filter(term == "movement_perc") %>%
  select(monkey, movement_parameter, estimate, std.error, statistic, p.value)

residual_movement_fit <- residual_movement_stats %>%
  unnest(glance) %>%
  select(monkey, movement_parameter, r.squared, adj.r.squared, p.value)

print("Coefficient statistics:")
print(residual_movement_coefs)

print("Model fit statistics:")
print(residual_movement_fit)
```



```{r}
sig_cells_string_all <- "Monkey U: 123 putative dopamine neurons; Monkey V: 145 putative dopamine neurons"
  
p_population_response_cells <- p_population_response +
  plot_annotation(
    title = '',
    subtitle = sig_cells_string_all,
  )
p_population_response_quintiles_cells <- p_population_response_quintiles +
  plot_annotation(
    title = '',
    subtitle = sig_cells_string_all,
  )

p_regressions <- (p_regression + theme(legend.position = "none", axis.text.x = element_blank(), axis.title.x = element_blank())) /
  p_norm_regression +
  plot_annotation(
    title = '',
    subtitle = sig_cells_string_all,
    tag_levels = "A"
  ) &   
  theme(
    legend.position = "bottom",
    plot.tag = element_text(size = 16)
  )

p_residuals <- p +  plot_annotation(
    title = '',
    subtitle = sig_cells_string_all,
  )   


```

```{r}
library(lme4)
library(lmerTest)

fd_trial_level <- fd_spikes %>%
  left_join(baselines, by = group_cols) %>%
  drop_na() %>%
  mutate(norm_n = (adj_n - mean_n) / sd_n) %>%
  left_join(
    select(bid_ntile_data, date, monkey, session, trial, monkey_bid),
    by = c("date", "monkey", "session", "trial")
  ) %>%
  mutate(
    bid_perc = monkey_bid / 100,
    cell_id  = paste(date, monkey, cell, sep = "_")
  )

me_results <- fd_trial_level %>%
  group_by(monkey) %>%
  group_modify(~ {
    m <- lmer(norm_n ~ bid_perc + (1|cell_id), data = .x, REML = FALSE)
    s <- summary(m)
    ct <- coef(s)
    tibble(
      intercept    = ct["(Intercept)", "Estimate"],
      intercept_se = ct["(Intercept)", "Std. Error"],
      slope        = ct["bid_perc", "Estimate"],
      slope_se     = ct["bid_perc", "Std. Error"],
      t_value      = ct["bid_perc", "t value"],
      p_value      = ct["bid_perc", "Pr(>|t|)"]
    )
  })

print(me_results)

p_me_regression <- p_me_regression +
  plot_annotation(
    title = '',
    subtitle = sig_cells_string_all
  )

ggsave(
  file.path("./Chapter4/Figs/redone_figs/", "fractal_display_lme_regression_fig.svg"),
  p_me_regression,
  width = 6.71,
  height = 7.5,
  units = "in"
)

```


ggsave(
  file.path("./output/redone_figs", "fractal_display_fig.svg"), 
  p_population_response_cells,
  width = 6.71,
  height = 6,
  units = "in"
)

ggsave(
  file.path("./output/redone_figs", "fractal_display_bids_fig.svg"), 
  p_population_response_quintiles_cells,
  width = 6.71,
  height = 6,
  units = "in"
)

ggsave(
  file.path("./output/redone_figs", "movement_residual.svg"), 
  p_residuals,
  width = 6.71,
  height = 7.5,
  units = "in"
)

ggsave(
  file.path("./output/redone_figs", "fractal_display_regression_fig.svg"), 
  p_regressions,
  width = 6.71,
  height = 7.5,
  units = "in"
)

```

