---
title: "free reward response"
author: "Robert Hickman"
---
title: "fractal display response"
author: "Robert Hickman"
date: "2025-03-12"
output: html_document
---

```{r setup, warning=FALSE,message=FALSE}
rm(list = ls())
set.seed(3459)
setwd("~/projects/thesis_scripts/figure_scripts/fractal_display/")
library(tidyverse)
library(jsonlite)
library(patchwork)
library(svglite)
library(viridis)
source("../../src/neuron_smoothing.R")
source("../../src/figs.R")

monkey_fill_pal <-
  scale_fill_manual(
    values = c("royalblue", "darkorange"),
    labels = c("Monkey U", "Monkey V"),
    guide = FALSE
  )
monkey_col_pal <-
  scale_colour_manual(
    values = c("royalblue", "darkorange"),
    labels = c("Monkey U", "Monkey V"),
    guide = FALSE
  )

neuronal_data <-
  readRDS("../../data/neurons/onefrac_noerror_neuronal_data.rds")
task_data <- readRDS("../../data/neurons/task_data.rds") %>%
    filter(situation %in% c(1,2,3)) %>%
    group_by(date, monkey, session) %>%
    mutate(fractals_shown = n_distinct(fractal_value), .groups = "drop") %>%
    filter(fractals_shown == 1)

cell_baselines_fractals <-
  readRDS("../../data/baseline/cell_prefc_baselines_fractals_smoothed.rds")
cell_baselines_fractal_counts <-
  readRDS("../../data/baseline/cell_prefc_baselines_fractals.rds")
cell_baselines_counts <-
  readRDS("../../data/baseline/cell_prefc_baselines.rds")

sigcells_uly <-
  read_csv("../../data/cells/uly_sig_cells.csv") %>%
  mutate(monkey = "Monkey U") %>%
  mutate(date = as.Date(date, "%d-%b-%y"))
sigcells_vice <-
  read_csv("../../data/cells/vice_sig_cells.csv") %>%
  mutate(monkey = "Monkey V") %>%
  mutate(date = as.Date(date, "%d-%b-%Y"))

sigcells <-
  bind_rows(sigcells_uly, sigcells_vice) %>%
  mutate(cell = paste0("cell", gsub("^(Clust)([0-9])(_.*)$", "\\2", cluster)))

window_end = 600
window_start = 100

monkey_windows <- read_csv("../../data/config/monkey_windows.csv")
configs <- read_csv("../../data/config/configs.csv")

group_cols <- c("date", "monkey", "cell")
group_cols_fractal <- c(group_cols, "fractal_value")

relevant_cells <- sigcells %>%
  select(date,
         monkey,
         cell,
         isDA,
         isResponsive,
         numTrGood,
         DAFracResponsive,
         DABidResponsive,
         DASigResponsive) %>%
  filter(isDA == 1 & isResponsive == 1 & numTrGood == 1) %>%
  distinct(date, monkey, cell, .keep_all = TRUE)

n_start <- filter(configs, var == "neurons_start") %>% pull(value)
n_end <- filter(configs, var == "neurons_end") %>% pull(value)
smooth_window <-
  filter(configs, var == "smooth_window") %>% pull(value)
```



```{r population_fig}
pre_start <- -500
pre_end <- -50

fractal_displayed_task_data <- task_data %>%
  filter(situation %in% c(1,2,3)) %>%
  select(date, monkey, trial, fractal_value, monkey_bid)

fd_bits <- neuronal_data %>%
  filter(situation %in% c(1,2,3)) %>%
  filter(map_lgl(bits, function(x) {
    if (!is.null(x) && is.data.frame(x) && nrow(x) > 0) {
      matching_rows <- x$names == "fractal_display" & x$index == "upat"
      sum(matching_rows) == 1 && !is.na(x$vals[matching_rows])
    } else {
      FALSE
    }
  })) %>%
  unnest(bits) %>%
  filter(names == "fractal_display" & index == "upat")

fd_spikes <- fd_bits %>%
  left_join(fractal_displayed_task_data, by = c("date", "monkey", "trial")) %>%
  filter(monkey_bid != 0 & monkey_bid != 100) %>%
  select(date, monkey, trial, fractal_value, fd_time = vals, sorted_spikes) %>%
  unnest(sorted_spikes) %>%
  mutate(spike_bit_time_ms = trial_spike_time_ms - fd_time)

fd_baselines <- fd_spikes %>%
  filter(spike_bit_time_ms >= pre_start & spike_bit_time_ms <= pre_end) %>%
  select(date, monkey, cell, fractal_value, spike_bit_time_ms) %>%
  group_by(date, monkey, cell, fractal_value) %>%
  group_split() %>%
  map_df(get_baseline_params, w = smooth_window, t = pre_start:pre_end)

fractal_display_smoothed <- fd_spikes %>%
  filter(spike_bit_time_ms >= n_start & spike_bit_time_ms <= n_end) %>%
  inner_join(relevant_cells, by = group_cols) %>%
  select(date, monkey, cell, fractal_value, spike_bit_time_ms) %>%
  nest(vector = spike_bit_time_ms) %>%
  left_join(fd_baselines, by = group_cols_fractal) %>%
  group_by(across(all_of(group_cols_fractal))) %>%
  group_split() %>%
  map_df(smooth_data, start = n_start, end = n_end, 100) %>%
  group_by(monkey, t, fractal_value) %>%
  summarise(
    av_zscore = mean(z_score, na.rm = TRUE),
    sd_zscore = sd(z_score, na.rm = TRUE),
    n = n(),
    .groups = "keep"
  ) %>%
  mutate(sem = sd_zscore / sqrt(n)) %>%
  mutate(fractal_reward_value = case_when(
    fractal_value == 1 ~ "low",
    fractal_value == 2 ~ "medium",
    fractal_value == 3 ~ "high"
  ))

p_population_response <-
  ggplot(
    fractal_display_smoothed %>% filter(
      t > filter(configs, var == "fig_start") %>% pull(value) &
        t < filter(configs, var == "fig_end") %>% pull(value)
    ),
    aes(x = t, y = av_zscore, colour = fractal_reward_value)
  ) +
  geom_rect(
    data = monkey_windows,
    aes(
      xmin = window_start,
      xmax = window_end,
      ymin = -Inf,
      ymax = Inf
    ),
    fill = "grey",
    alpha = 0.5,
    inherit.aes = FALSE
  ) +
  geom_line() +
  scale_colour_manual(values = c("darkgreen"),
                      name = "fractal reward value") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  facet_wrap( ~ monkey, scales = "free") +
  population_firing_fig_theme(
    filter(configs, var == "fig_start") %>% pull(value),
    filter(configs, var == "fig_end") %>% pull(value),
    "fractal display"
  )

```

```{r population_fig}
bid_splits <- 3
pre_start <- -500
pre_end <- -50


bid_quintile_task_data <- task_data %>%
  filter(is.na(error_bit)) %>%
  filter(situation %in% c(1, 2, 3)) %>%
  select(date, monkey, trial, monkey_bid) %>%
  mutate(
    monkey_bid_quintile = case_when(
      monkey_bid < 33 ~ 1,
      monkey_bid < 66 ~ 2,
      monkey_bid >= 66 & monkey_bid <= 100 ~ 3
    )
  )

fd_spikes <- fd_bits %>%
  left_join(bid_quintile_task_data, by = c("date", "monkey", "trial")) %>%
  filter(monkey_bid != 0 & monkey_bid != 100) %>%
  select(date,
         monkey,
         trial,
         monkey_bid_quintile,
         fd_time = vals,
         sorted_spikes) %>%
  unnest(sorted_spikes) %>%
  mutate(spike_bit_time_ms = trial_spike_time_ms - fd_time)

fd_baselines <- fd_spikes %>%
  filter(spike_bit_time_ms >= pre_start &
           spike_bit_time_ms <= pre_end) %>%
  select(date, monkey, cell, monkey_bid_quintile, spike_bit_time_ms) %>%
  group_by(date, monkey, cell, monkey_bid_quintile) %>%
  group_split() %>%
  map_df(get_baseline_params, w = smooth_window, t = pre_start:pre_end)

uly_cells <- fd_spikes %>%
  filter(monkey == "Monkey U") %>%
  inner_join(relevant_cells, by = group_cols) %>%
  filter(DABidResponsive == 1 | DAFracResponsive == 1 | DASigResponsive == 1)

vice_cells <- fd_spikes %>%
  filter(monkey == "Monkey V")

fractal_display_smoothed <- 
  bind_rows(uly_cells, vice_cells) %>%
  filter(spike_bit_time_ms >= n_start &
           spike_bit_time_ms <= n_end) %>%
  select(date, monkey, cell, monkey_bid_quintile, spike_bit_time_ms) %>%
  nest(vector = spike_bit_time_ms) %>%
  left_join(fd_baselines, by = c(group_cols, "monkey_bid_quintile")) %>%
  group_by(across(all_of(c(
    group_cols, "monkey_bid_quintile"
  )))) %>%
  group_split() %>%
  map_df(smooth_data, start = n_start, end = n_end, 100) %>%
  group_by(monkey, t, monkey_bid_quintile) %>%
  summarise(
    av_zscore = mean(z_score, na.rm = TRUE),
    sd_zscore = sd(z_score, na.rm = TRUE),
    n = n(),
    .groups = "keep"
  ) %>%
  mutate(sem = sd_zscore / sqrt(n))

p_population_response_quintiles <-
  ggplot(
    fractal_display_smoothed %>% filter(
      t > filter(configs, var == "fig_start") %>% pull(value) &
        t < filter(configs, var == "fig_end") %>% pull(value)
    ),
    aes(
      x = t,
      y = av_zscore,
      colour = factor(monkey_bid_quintile)
    )
  ) +
  geom_rect(
    data = monkey_windows,
    aes(
      xmin = window_start,
      xmax = window_end,
      ymin = -Inf,
      ymax = Inf
    ),
    fill = "grey",
    alpha = 0.5,
    inherit.aes = FALSE
  ) +
  geom_line() +
  scale_colour_manual(values = viridis::inferno(bid_splits, begin = 0, end = 0.8),
                      name = "forthcoming bid tercile (3 highest)") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  facet_wrap(~ monkey, scales = "free") +
  population_firing_fig_theme(
    filter(configs, var == "fig_start") %>% pull(value),
    filter(configs, var == "fig_end") %>% pull(value),
    "fractal display"
  )

spike_counts <- fd_spikes %>%
  select(date, monkey, cell, trial, monkey_bid_quintile, spike_bit_time_ms) %>%
  left_join(monkey_windows, by = "monkey") %>%
  group_by(date, monkey, cell, trial, monkey_bid_quintile, window_start, window_end) %>%
  summarise(n = sum(spike_bit_time_ms >= window_start & spike_bit_time_ms <= window_end), .groups = "drop") %>%
  mutate(adj_n = n * (1000 / (window_end - window_start))) %>%
  right_join(relevant_cells, by = group_cols) %>%
  drop_na() %>%
  mutate(adj_n = replace_na(adj_n ,0)) %>%
  select(date, monkey, cell, trial, monkey_bid_quintile, spike_counts = adj_n)
  
agg_spike_counts <- spike_counts %>%
  group_by(date, monkey, cell, monkey_bid_quintile) %>%
  summarise(mean_spike_counts = mean(spike_counts), sem_spike_counts = sd(spike_counts) / sqrt(n()), n_trials = n(), .groups = "drop")


monkey_u_data <- subset(agg_spike_counts, monkey == "Monkey U")
monkey_v_data <- subset(agg_spike_counts, monkey == "Monkey V")

kw_u <- kruskal.test(mean_spike_counts ~ factor(monkey_bid_quintile), data = monkey_u_data)
print("Kruskal-Wallis Test Results for Monkey U:")
print(kw_u)

kw_v <- kruskal.test(mean_spike_counts ~ factor(monkey_bid_quintile), data = monkey_v_data)
print("Kruskal-Wallis Test Results for Monkey V:")
print(kw_v)

relevant_cells_one_frac <- relevant_cells %>%
  inner_join(task_data %>% select(date, monkey) %>% distinct(), by = c("date", "monkey")) %>%
  filter(DABidResponsive == 1) %>%
  pull(monkey) %>%
  table()
```

```{r}
ntiles = 25

bid_ntile_data <- task_data %>%
  filter(situation %in% c(1, 2, 3)) %>%
  filter(monkey_bid !=0 & monkey_bid != 100) %>%
  select(date, monkey, session, trial, monkey_bid) %>%
  mutate(
    bid_ntiles = cut(
      monkey_bid,
      breaks = seq(0, 100, by = 100/ntiles),
      labels = FALSE,
      include.lowest = TRUE
    )
  )

ntile_trials <- bid_ntile_data %>%
  group_by(monkey, bid_ntiles) %>%
  summarise(trials = n(), .groups = "drop")

relevant_cells_ntiles <- relevant_cells %>%
  filter(monkey == "Monkey U" | DABidResponsive == 1) %>%
  select(all_of(group_cols)) %>%
  crossing(bid_ntiles = 1:ntiles) %>%
  filter(
    !(monkey == "Monkey U" & bid_ntiles %in% c(1)),
    !(monkey == "Monkey V" & bid_ntiles %in% c(1:7)),
  )

fd_spikes <- fd_bits %>%
  left_join(bid_ntile_data, by = c("date", "monkey", "session", "trial")) %>%
  select(date, monkey, session, trial, bid_ntiles, fd_time = vals, sorted_spikes) %>%
  unnest(sorted_spikes) %>%
  mutate(spike_bit_time_ms = trial_spike_time_ms - fd_time) %>%
  group_by(date, monkey, cell, session, trial, bid_ntiles) %>%
  summarise(n = sum(spike_bit_time_ms >= window_start & spike_bit_time_ms <= window_end), .groups = "drop") %>%
  mutate(adj_n = n * (1000 / (window_end - window_start))) %>%
  right_join(relevant_cells_ntiles, by = c(group_cols, "bid_ntiles")) %>%
  mutate(adj_n = replace_na(adj_n ,0))

fd_av_spikes <- fd_spikes %>%
  group_by(monkey, bid_ntiles) %>%
  summarise(mean_n_s = mean(adj_n), sem = sd(adj_n) / sqrt(n()), .groups = "drop") %>%
  mutate(bid_perc = bid_ntiles / ntiles) %>%
  inner_join(ntile_trials, by = c("monkey", "bid_ntiles"))

regression_stats <- fd_av_spikes %>%
  group_by(monkey) %>%
  do(model = lm(mean_n_s ~ bid_perc, data = .)) %>%
  mutate(
    glance = list(broom::glance(model))
  ) %>%
  unnest(glance) %>%
  select(monkey, p.value, r.squared, adj.r.squared)

print(regression_stats)

p_regression <- ggplot(fd_av_spikes, aes(x = bid_perc, y = mean_n_s, colour = monkey, group = monkey)) + 
  stat_smooth(method = "lm") +
  geom_point(size = 2) + 
  geom_errorbar(aes(ymin = mean_n_s - sem, ymax = mean_n_s + sem), width = 0) +
  monkey_col_pal +
  labs(
    x = "monkey bid percentage",
    y = "average firing rate (impulses/s)"
  ) +
  theme_minimal() +
  facet_wrap(~ monkey, scales = "free_y") +
  theme(
    strip.background = element_blank(),
    strip.text = element_blank(),
    legend.position = "bottom"
  ) +
  scale_x_continuous(limits = c(0, 1))

baselines <- cell_baselines_counts %>%
  inner_join(relevant_cells, by = group_cols) %>%
  group_by(date, monkey, cell, trial) %>%
  summarise(n = sum(spike_bit_time_ms >= -500 & spike_bit_time_ms <= 0), .groups = "drop") %>%
  mutate(adj_n = n * 2) %>%
  group_by(date, monkey, cell) %>%
  summarise(mean_n = mean(adj_n), sd_n = sd(adj_n), .groups = "drop") %>%
  filter(sd_n != 0)

baselines2 <- fd_bits %>%
  left_join(bid_ntile_data, by = c("date", "monkey", "session", "trial")) %>%
  select(date, monkey, session, trial, bid_ntiles, fd_time = vals, sorted_spikes) %>%
  unnest(sorted_spikes) %>%
  mutate(spike_bit_time_ms = trial_spike_time_ms - fd_time) %>%
  filter(spike_bit_time_ms > -550 & spike_bit_time_ms < -50) %>%
  group_by(date, monkey, cell, trial) %>%
  summarise(n = sum(spike_bit_time_ms >= -550 & spike_bit_time_ms <= -50), .groups = "drop") %>%
  mutate(adj_n = n * 2) %>%
  group_by(date, monkey, cell) %>%
  summarise(mean_n = mean(adj_n), sd_n = sd(adj_n), .groups = "drop") %>%
  filter(sd_n != 0)

spikes_uly <- fd_spikes %>%
  filter(monkey == "Monkey U") %>%
  left_join(baselines2, by = group_cols)
spikes_vice <- fd_spikes %>%
  filter(monkey == "Monkey V") %>%
  left_join(baselines, by = c(group_cols)) %>%
  drop_na()

fd_normalised_spikes <- bind_rows(spikes_uly, spikes_vice) %>%
  drop_na() %>%
  mutate(norm_n = (adj_n - mean_n) / sd_n) %>%
  group_by(monkey, bid_ntiles) %>%
  summarise(mean_n_s = mean(norm_n), sem = sd(norm_n) / sqrt(n()), .groups = "drop") %>%
  mutate(bid_perc = bid_ntiles / ntiles) %>%
  inner_join(ntile_trials, by = c("monkey", "bid_ntiles"))

regression_stats_norm <- fd_normalised_spikes %>%
  group_by(monkey) %>%
  do(model = lm(mean_n_s ~ bid_perc, data = .)) %>%
  mutate(
    glance = list(broom::glance(model))
  ) %>%
  unnest(glance) %>%
  select(monkey, p.value, r.squared, adj.r.squared)

print(regression_stats_norm)

p_norm_regression <- ggplot(fd_normalised_spikes, aes(x = bid_perc, y = mean_n_s, colour = monkey, group = monkey)) + 
  stat_smooth(method = "lm") +
  geom_point(size = 2) + 
  geom_errorbar(aes(ymin = mean_n_s - sem, ymax = mean_n_s + sem), width = 0) +
  monkey_col_pal +
  labs(
    x = "monkey bid percentage",
    y = "normalised firing rate (impulses/s)"
  ) +
  theme_minimal() +
  facet_wrap(~ monkey, scales = "free_y") +
  theme(
    strip.background = element_blank(),
    strip.text = element_blank(),
    legend.position = "bottom"
  ) +
  scale_x_continuous(limits = c(0, 1))

```


```{r}
sig_cells_string_one <- "Monkey U: 21 putative dopamine neurons; Monkey V: 24 putative dopamine neurons"

p_population_response <- p_population_response +
  plot_annotation(
    title = '',
    subtitle = sig_cells_string_one,
  )
p_population_response_quintiles <- p_population_response_quintiles +
  plot_annotation(
    title = '',
    subtitle = sig_cells_string_one,
  )

p_regressions <- (p_regression + theme(legend.position = "none", axis.text.x = element_blank(), axis.title.x = element_blank())) / p_norm_regression +
  plot_annotation(title = '',
                  subtitle = sig_cells_string_one,
                  tag_levels = "A")
```


```{r corrections}
# --- Category E: single- vs multi-fractal session dopamine comparison (medium fractal) ---

neuronal_data_3frac <-
  readRDS("../../projects/thesis_scripts/data/neurons/threefrac_noerror_neuronal_data.rds")
neuronal_data_cmp <- bind_rows(neuronal_data, neuronal_data_3frac)

task_data_cmp <- readRDS("../../projects/thesis_scripts/data/neurons/task_data.rds") %>%
  filter(situation %in% c(1,2,3)) %>%
  group_by(date, monkey, session) %>%
  mutate(fractals_shown = n_distinct(fractal_value)) %>%
  ungroup() %>%
  filter(fractals_shown %in% c(1,3)) %>%
  filter(fractal_value == 2) %>%
  select(date, monkey, session, trial, fractal_value, monkey_bid, fractals_shown)

fd_bits_cmp <- neuronal_data_cmp %>%
  filter(situation %in% c(1,2,3)) %>%
  filter(map_lgl(bits, function(x) {
    if (!is.null(x) && is.data.frame(x) && nrow(x) > 0) {
      matching_rows <- x$names == "fractal_display" & x$index == "upat"
      sum(matching_rows) == 1 && !is.na(x$vals[matching_rows])
    } else FALSE
  })) %>%
  unnest(bits) %>%
  filter(names == "fractal_display" & index == "upat")

fd_spikes_cmp <- fd_bits_cmp %>%
  left_join(task_data_cmp, by = c("date", "monkey", "session", "trial")) %>%
  filter(!is.na(fractals_shown)) %>%
  filter(monkey_bid != 0 & monkey_bid != 100) %>%
  select(date, monkey, session, trial, fractals_shown, fd_time = vals, sorted_spikes) %>%
  unnest(sorted_spikes) %>%
  mutate(spike_bit_time_ms = trial_spike_time_ms - fd_time) %>%
  group_by(date, monkey, cell, trial, fractals_shown) %>%
  summarise(n = sum(spike_bit_time_ms >= window_start & spike_bit_time_ms <= window_end), .groups = "drop") %>%
  mutate(adj_n = n * (1000 / (window_end - window_start))) %>%
  inner_join(relevant_cells %>% select(all_of(group_cols)) %>% distinct(), by = group_cols)

baselines2_cmp <- fd_bits_cmp %>%
  left_join(task_data_cmp, by = c("date", "monkey", "session", "trial")) %>%
  filter(!is.na(fractals_shown)) %>%
  select(date, monkey, session, trial, fd_time = vals, sorted_spikes) %>%
  unnest(sorted_spikes) %>%
  mutate(spike_bit_time_ms = trial_spike_time_ms - fd_time) %>%
  filter(spike_bit_time_ms > -550 & spike_bit_time_ms < -50) %>%
  group_by(date, monkey, cell, trial) %>%
  summarise(n = sum(spike_bit_time_ms >= -550 & spike_bit_time_ms <= -50), .groups = "drop") %>%
  mutate(adj_n = n * 2) %>%
  group_by(date, monkey, cell) %>%
  summarise(mean_n = mean(adj_n), sd_n = sd(adj_n), .groups = "drop") %>%
  filter(sd_n != 0)

spikes_uly_cmp  <- fd_spikes_cmp %>% filter(monkey == "Monkey U") %>% left_join(baselines2_cmp, by = group_cols)
spikes_vice_cmp <- fd_spikes_cmp %>% filter(monkey == "Monkey V") %>% left_join(baselines, by = group_cols) %>% drop_na()

fd_norm_cmp <- bind_rows(spikes_uly_cmp, spikes_vice_cmp) %>%
  drop_na() %>%
  mutate(norm_n = (adj_n - mean_n) / sd_n)

fd_norm_cmp %>% distinct(date, monkey, cell, fractals_shown) %>% count(monkey, fractals_shown) %>% print()

# --- stats: trial-level Wilcoxon + Cohen's d, mirrors the behavioural d=0.467/0.077 test ---
library(effsize)

wilcox_trial <- fd_norm_cmp %>%
  group_by(monkey) %>%
  group_split() %>%
  map_df(function(dat) {
    x <- filter(dat, fractals_shown == 3)$norm_n
    y <- filter(dat, fractals_shown == 1)$norm_n
    broom::tidy(wilcox.test(x, y)) %>% mutate(monkey = unique(dat$monkey))
  })

cohens_trial <- fd_norm_cmp %>%
  group_by(monkey) %>%
  group_split() %>%
  map_df(function(dat) {
    x <- filter(dat, fractals_shown == 3)$norm_n
    y <- filter(dat, fractals_shown == 1)$norm_n
    d <- cohen.d(x, y)
    tibble(monkey = unique(dat$monkey), cohens_d = d$estimate, magnitude = as.character(d$magnitude))
  })

print(wilcox_trial)
print(cohens_trial)

# --- stats: LME (cell-level random effect) ---
library(lmerTest)

fd_norm_cmp <- fd_norm_cmp %>%
  mutate(cell_id = paste(date, monkey, cell, sep = "_"))

me_results_cmp <- fd_norm_cmp %>%
  group_by(monkey) %>%
  group_split() %>%
  map_df(function(dat) {
    model <- lmer(norm_n ~ factor(fractals_shown) + (1 | cell_id), data = dat, REML = FALSE)
    coefs <- summary(model)$coefficients
    tibble(
      monkey = unique(dat$monkey),
      estimate = coefs[2, "Estimate"],
      se = coefs[2, "Std. Error"],
      p_value = coefs[2, "Pr(>|t|)"]
    )
  })

print(me_results_cmp)

# --- stats: Bayes factor on per-cell means (independent samples — cells not paired across session types) ---
library(BayesFactor)

percell_cmp <- fd_norm_cmp %>%
  group_by(monkey, date, cell, fractals_shown) %>%
  summarise(mean_norm_n = mean(norm_n), .groups = "drop")

bf_cmp <- percell_cmp %>%
  group_by(monkey) %>%
  group_split() %>%
  map_df(function(dat) {
    x <- filter(dat, fractals_shown == 3)$mean_norm_n
    y <- filter(dat, fractals_shown == 1)$mean_norm_n
    bf <- ttestBF(x = x, y = y)
    tibble(monkey = unique(dat$monkey), bf10 = extractBF(bf)$bf, bf01 = 1 / extractBF(bf)$bf)
  })

print(bf_cmp)

```

```{r corrections2}
fd_norm_trial_single <- bind_rows(spikes_uly, spikes_vice) %>%
  drop_na() %>%
  mutate(
    norm_n = (adj_n - mean_n) / sd_n,
    bid_perc = bid_ntiles / ntiles,
    cell_id = paste(date, monkey, cell, sep = "_")
  )

me_results_bid_single <- fd_norm_trial_single %>%
  group_by(monkey) %>%
  group_split() %>%
  map_df(function(dat) {
    model <- lmer(norm_n ~ bid_perc + (1 | cell_id), data = dat, REML = FALSE)
    coefs <- summary(model)$coefficients
    tibble(
      monkey = unique(dat$monkey),
      n_trials = nrow(dat),
      estimate = coefs[2, "Estimate"],
      se = coefs[2, "Std. Error"],
      p_value = coefs[2, "Pr(>|t|)"]
    )
  })

print(me_results_bid_single)



```


ggsave(
  file.path("./output/redone_figs", "one_fractal_display_fig.svg"), 
  p_population_response,
  width = 6.71,
  height = 6,
  units = "in"
)

ggsave(
  file.path("./output/redone_figs", "one_fractal_display_bids_fig.svg"), 
  p_population_response_quintiles,
  width = 6.71,
  height = 6,
  units = "in"
)

ggsave(
  file.path("./output/redone_figs", "one_fractal_display_regression_fig.svg"), 
  p_regressions,
  width = 6.71,
  height = 7.5,
  units = "in"
)

```

